\chapter{Data Visualization and Storytelling with Tableau}
\label{chapter:Data Visualization and Storytelling with Tableau}

\section{Initial Dataset Evaluation}

Once I downloaded and extracted the dataset, I began by evaluating its structure and format. During this initial assessment, I encountered several issues:

\begin{itemize}
    \item \textbf{Lack of Column Headers}: The dataset lacked a clear header row to indicate the purpose of each column.
    \item \textbf{No Date Column}: There was no dedicated column for dates, which was essential for accurate analysis.
    \item \textbf{Merged Cells for Visual Aesthetics}: Several cells were merged solely for visual formatting, which interfered with data processing.
    \item \textbf{Redundant Data Column}: One column contained the word \textbf{“Water”} in every cell, serving no analytical purpose. I removed this column to streamline the dataset.
\end{itemize}

Additionally, the files within the dataset were in varied formats:

\begin{itemize}
    \item Some files were in \textbf{HTML} or \textbf{MHT} formats, which are not directly compatible with most data tools.
    \item Other files were saved in \textbf{Excel 97 (XLS)} format, an outdated version that did not support the latest formatting features.
\end{itemize}

I addressed these issues by applying the necessary modifications in excel itself and then saved all files in the updated \textbf{XLSX} format for consistency and ease of use.

\section{Visualizations Overview}

\section{Interactive Dashboard Design}

\section{Data Storytelling and Key Insights}